---
title: "EDA-2: Contextual Predisposing"
author: "Andriy Koval"
date: "May 9, 2020"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: false
    toc_float: true
    code_folding: hide
---

# Abstract
This report explores the Contextual Predisposing Characteristics (see Anderson model) of OECD countries and relates them to COVID-19 mortality during the first 30 days of the epidemic in each country. 

The report will focus on three subsections: (1) Demographic characteristics, (2) Social characteristic, and (3) Belief, as operationalized by the variables in the OECD database. 

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') # "go up" from the folder where this .Rmd is save until you arrive at the root/working directory
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  attr.source = ".numberLines",
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  # fig.height = 4, 
  # fig.width = 5.5, 
  # out.width = "700px",
  fig.path = 'figure_rmd/'     
  # dev = "png"
  # dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/eda-4/eda-4.R")
# read_chunk("../../../analysis/blogposts/florida-suicide-count/fl-suicide-count.R")
```

# Environment

```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```
 
```{r declare-functions, echo=echoChunks, results='show', message=FALSE}
```

# Data  

The data comes from [OxCGRT][] and  [OECD][] databases

```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

## Data Tweaks

```{r tweak-data-1, echo=echoChunks, results='show', message=FALSE,cache=TRUE, warning =F}
# ds0 %>% glimpse()
```

# COVID Indicators

What are some basic indicators of progression of COVID in each country?  Without resorting to estimating the growth parameter of the contagion or mortality trajectory, we compute impact indicators based on the total number of cases or deaths at a given time point:   

__RELATIVE__ time points  
- Number of __deaths__ 30 days since 1st confirmed ___death___ (per 1 million)
- Number of __deaths__ 30 days since 1st confirmed ___case___ (per 1 million)
- Number of __cases__ 30 dyas since 1st confirmed ___death___ (per 1 million)
- Number of __cases__ 30 dyas since 1st confirmed ___case___ (per 1 million)

__ABSOLUTE__ time points  
- Number of __deaths__ 100 days since Exodus (per 1 million)
- Number of __cases__ 100 days since Exodus (per 1 million)

__DURATION__ metrics  
- Number of __days__ from Exodus to 1st Case 
- Number of __days__ from Exodus to 1st Death 

```{r covid-metric-1, echo=TRUE, fig.height=7, fig.width=10, out.width = "1200px", message=FALSE, results='hide',warning = F, cache=TRUE}
```

  
  

session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
