---
title: "COVID-19 in USA - John Hopkins Data"
author: "Andriy Koval"
date: "October 1, 2020"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: false
    toc_float: true
    code_folding: hide
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') # "go up" from the folder where this .Rmd is save until you arrive at the root/working directory
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  attr.source = ".numberLines",
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  # fig.height = 4, 
  # fig.width = 5.5, 
  # out.width = "700px",
  fig.path = 'figure_rmd/'     
  # dev = "png"
  # dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/us-response/us-response-1.R")
# read_chunk("../../../analysis/blogposts/florida-suicide-count/fl-suicide-count.R")
```


```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```
 
```{r declare-functions, echo=echoChunks, results='show', message=FALSE}
```


```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data, echo=echoChunks, results='show', message=FALSE, warning=F}
```

# Timeline of COVID-19 measures

Source: [COVID-19 Data Repository by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19)

See [codebook](https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data#usa-daily-state-reports-csse_covid_19_daily_reports_us) for definition of measures. 

* <b>Confirmed</b> - Aggregated case count for the state.
* <b>Incident_Rate</b> - cases per 100,000 persons.

* <b>Deaths</b> - Aggregated death toll for the state.
* <b>Mortality_Rate</b> - Number recorded deaths * 100/ Number confirmed cases.

* <b>People_Tested</b> - Total number of people who have been tested.
* <b>Testing_Rate</b> - Total test results per 100,000 persons. The "total test results" are equal to "Total test results (Positive + Negative)" from [COVID Tracking Project](https://covidtracking.com/).

* <b>People_Hospitalized</b> - Total number of people hospitalized. (Nullified on Aug 31, see [Issue #3083](https://github.com/CSSEGISandData/COVID-19/issues/3083))
* <b>Hospitalization_Rate</b> - US Hospitalization Rate (%): = Total number hospitalized / Number cases. The "Total number hospitalized" is the "Hospitalized – Cumulative" count from [COVID Tracking Project](https://covidtracking.com/). The "hospitalization rate" and "Total number hospitalized" is only presented for those states which provide cumulative hospital data. (Nullified on Aug 31, see 

* <b>Recovered</b> - Aggregated Recovered case count for the state.
* <b>Active</b> - Aggregated confirmed cases that have not been resolved (Active cases = total cases - total recovered - total deaths).

## Confirmed 

```{r confirmed, echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```


## Deaths 

```{r deaths,echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```


## Tests

 
```{r tested,echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```


## Hospitalizations

 
```{r hospitalized,echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```



session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
