---
title: "EDA-1"
author: "Andriy Koval"
date: "May 7, 2020"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: true
    toc_float: true
    code_folding: hide
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') # "go up" from the folder where this .Rmd is save until you arrive at the root/working directory
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  attr.source = ".numberLines",
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  # fig.height = 4, 
  # fig.width = 5.5, 
  # out.width = "700px",
  fig.path = 'figure_rmd/'     
  # dev = "png"
  # dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/eda-1/eda-1.R")
# read_chunk("../../../analysis/blogposts/florida-suicide-count/fl-suicide-count.R")
```
# Abstract

The reports looks at progression of COVID-19 within OECD countries and the overall magnitude of governments' response to the pandemic. 

# Environment

```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```
 
```{r declare-functions, echo=echoChunks, results='show', message=FALSE}
```

# Data Sources 

- Cases and mortlaity for COVID-19 are sourced from the [European Centre for Disease Prevention and Control](https://www.ecdc.europa.eu/en/covid-19-pandemic) 
- Government Response metric to COVID-19 (Stringency Index) is sources from [Oxford COVID-19 Government Response Tracker (OxCGRT)](https://www.bsg.ox.ac.uk/research/research-projects/coronavirus-government-response-tracker)


```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data-1, echo=echoChunks, results='show', message=FALSE,cache=TRUE, warning =F}
ds0 %>% glimpse()
```

# Q0 - Response and Toll

> What does Response to and Toll from COVID look for all OECD countries?

## Response 

```{r q3-response-all,echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```
.  
.  
.  
.  
.  
.    

## Toll   


```{r q3-toll-all, echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```

.  
.  
.  
.  
.  


## Toll centered   

```{r q3-toll-all-centered, echo=TRUE,  message=FALSE, results='show',warning = F, cache=TRUE}
```
.  
.  
.  
.  
.   

# Q1 - Shape of the trend

> How does COVID-19 progress in each country?  

```{r q1-basic-timeline, echo=TRUE, fig.height=8, fig.width=10, out.width = "1200px", message=FALSE, results='asis',warning = F, cache=TRUE}
```

# Q1 - Within Country

> How do key indices compare within each country?

___Common legend___:  

- (first dot) = 1st confirmed case
- (second dot) = 1st confirmed death  
- (dotted line) = pandemic announced by WHO (March 11)  
- (dashed lines) = 75th and 100th day since Exodus (January 13), first confirmed case outside China  
- X-asis measures `Days since Exodus`

```{r q1a, echo=TRUE, fig.height=2, fig.width=10, out.width = "1200px", message=FALSE, results='asis',warning = F, cache=TRUE}
```

# Q2 - Response 

> What was the trend of the response to COVID-10 by each country?  

```{r q2-response-trend, echo=TRUE, fig.height=7, fig.width=10, out.width = "1200px", message=FALSE, results='asis',warning = F, cache=TRUE}
```







session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
