---
title: "Response Stringency (2)"
author: "Andriy Koval"
date: "May 11, 2020"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: true
    toc_float: true
    code_folding: hide
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') # "go up" from the folder where this .Rmd is save until you arrive at the root/working directory
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  attr.source = ".numberLines",
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "1200px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/response-stringency-2/response-stringency-2.R")
# read_chunk("../../../analysis/blogposts/florida-suicide-count/fl-suicide-count.R")
```
# Abstract

Using the data from the [OxCGRT][] we explore the typology of policy response by each government to COVID-19 pandemic

# Environment

```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```
 
```{r declare-functions, echo=echoChunks, results='show', message=FALSE}
```

# Data  

The data comes from [OxCGRT][] and  [OECD][] databases

```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

## Data Tweaks

```{r tweak-data-1, echo=echoChunks, results='show', message=FALSE,cache=TRUE, warning =F}
ds0 %>% glimpse()
```

# Q1 - Shape of the trend

> How does COVID-19 progress in each country?  

```{r q1, echo=TRUE, fig.height=7, fig.width=10, out.width = "1200px", message=FALSE, results='asis',warning = F, cache=TRUE}
```


session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
